### 2022-11-19 introduction/introduction.tex
Polished up some sentences in introduction

Life is a physical phenomenon. Despite the complexity of the cells, tissues, and organs that compose living things, all these processes are governed by the same physical laws that describe how the planets revolve around the sun and the probability that an atom of uranium decays from one moment to another. However, as many systems are too complex to describe with physical models and equations, scientists simplify to achieve levels of abstraction that are more useful. (This is the origin of the common observation that biology is applied chemistry and chemistry is applied physics.) Since life spans a scale from the size of single cell to entire ecosystems, biology likely employs more layers of abstraction than any other scientific discipline. One of the most powerful and widely used frameworks within the life sciences is biochemistry, which characterizes biological processes in terms of their component molecules. A specific focus is four classes of macromolecules called nucleic acids, carbohydrates, lipids, and proteins, all of which are unique to biological systems. Though not all biological molecules are macromolecules and not all biological macromolecules fit neatly in one of these four categories, much of life at the molecular level is understood in terms of their structure and function. Each of the four has a characteristic role. Nucleic acids, i.e. DNA and RNA, are responsible for information storage and transfer. Carbohydrates primarily store energy but can also act as structural components of cells. Lipids are a diverse class of oily molecules which are components of cell membranes, store energy, and transmit signals. Proteins have a diverse range of functions including but not limited to catalyzing reactions, transmitting signals, and providing structure. Proteins have such a diverse range of associated functions, many of which overlap with the other three categories, because proteins are involved in virtually every biological process. Moreover, proteins are highly dynamic. They respond to signals, change shape, and even use the other macromolecules as raw material for their activities. In this way, proteins are like molecular machines.

@@

>>>>

Life is a physical phenomenon. Despite the complexity of living things, all these processes are governed by the same physical laws that describe how the planets revolve around the sun and the probability that an atom of uranium decays from one moment to another. However, as many systems are too complex to describe with physical models and equations, scientists simplify these details into levels of abstraction that are more useful. (This is the origin of the common observation that biology is applied chemistry and chemistry is applied physics.) Since life spans a scale from a single cell to entire ecosystems, biology likely employs more layers of abstraction than any other scientific discipline. One of the most powerful and widely used frameworks within the life sciences is biochemistry, which characterizes biological processes in terms of their component molecules. A specific focus is four classes of macromolecules called nucleic acids, carbohydrates, lipids, and proteins, all of which are unique to biological systems. Though not all biological molecules are macromolecules and not all biological macromolecules fit neatly in one of these four categories, much of life at the molecular level is understood in terms of their structure and function. Each of the four has a characteristic role. Nucleic acids, i.e., DNA and RNA, are responsible for information storage and transfer. Carbohydrates primarily store energy but can also act as structural components of cells. Lipids are a diverse class of oily molecules which are components of cell membranes, store energy, and transmit signals. Proteins have a range of functions, including catalyzing reactions, transmitting signals, and providing structure. Many of these overlap with the functions of the other macromolecule classes because proteins are involved in virtually every biological process. However, unlike the others, which are often passive participants, proteins are highly active and dynamic. They respond to signals, change shape, and even use the other macromolecules as raw material. Proteins are therefore the molecular machines that carry out a cell's activities.

@@

To illustrate these concepts,
